Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-23 ms.tex
a few words for the systematic FP

EPIC 201555883 is a unique case in that it does not appear to fall under any of these
cases. It falls on module 23, while EPIC 201569483 is on module 8, neither 180 degrees
away from nor on the same column as this candidate.
Moreover, there is not any evidence of a mechanism that could cause a third star to
induce both the appearance of a $7\%$ eclipse on one module and an additional
anomalous transit event on a different module.

>>>>

EPIC 201555883 is a unique case in that it does not appear to fall under any
of these cases. It falls on module 23, while EPIC 201569483 is on module 8,
neither 180 degrees away from nor on the same column as this candidate.
Moreover, there is not any evidence of a mechanism that could cause a third
star to induce both the appearance of a $7\%$ eclipse on one module and an
additional anomalous transit event on a different module.
Instead, this candidate could be a false positive caused by a different
systematic mechanism.
\paperit\ modeled the systematic effects in the \KT\ light curves using a
linear combination of ``eigen light curves'' generated empirically by running
a principle component analysis on the light curves of every star.
This means that the training set includes the light curves for variable stars,
eclipsing binaries, and even transiting planets.
